% Resume.tex - Condensed 1-page, 2-column version
% Blair G. — Software Engineer / Product Manager

\documentclass[9pt]{article}
\usepackage[top=1in, bottom=1in, left=1in, right=1in]{geometry}
\usepackage{multicol}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{parskip}
\usepackage[hidelinks]{hyperref}
\usepackage{ragged2e}   % add to preamble

% Disable hyphenation
\usepackage[none]{hyphenat}
\usepackage{fancyhdr} %%For headers/footers
\hyphenpenalty=10000
\exhyphenpenalty=10000
\raggedbottom
\pagenumbering{gobble}

\titleformat{\section}{\Large\bfseries}{}{0em}{}
\titleformat{\subsection}{\normalsize\bfseries}{}{0em}{}

\begin{document}

% -------------------- HEADER --------------------
%\begin{center}
%    {\LARGE \textbf{Blair Gemmer}} \\[0.25em]
%    \href{mailto:blair.gemmer@gmail.com}{blair.gemmer@gmail.com} $\vert$ 406.253.4962 $\vert$ Missoula, MT \\
%    \href{https://blairgemmer.com}{blairgemmer.com} $\vert$ \href{https://linkedin.com/in/blairgemmer}{linkedin.com/in/blairgemmer} $\vert$ \href{https://github.com/blairg23}{github.com/blairg23}
%\end{center}

\pagestyle{fancy}           % ← this makes the header/footer appear
% \thispagestyle{fancy}     % also add this if the résumé stays one-page
\renewcommand{\footrulewidth}{1pt}

%Header / Footer information:
\fancyhead[L]{\Huge{Blair Gemmer} \small{\{\href{https://blairgemmer.com}{blairgemmer.com} --  \href{mailto:blair.gemmer@gmail.com}{blair.gemmer@gmail.com} -- \href{tel:4062534962}{406.253.4962}\}} \hfill \copyright \ \the\year} %%Header
\fancyfoot[L]{\small{\{\href{https://blairgemmer.com}{blairgemmer.com} --  \href{mailto:blair.gemmer@gmail.com}{blair.gemmer@gmail.com} -- \href{tel:4062534962}{406.253.4962}\}} \hfill v2025.06.16} %Footer



% Two-column layout with ragged columns to avoid hyphenation
\begin{multicols}{2}
\raggedcolumns
\RaggedRight  

% -------------------- SUMMARY --------------------
\noindent
\textbf{\large Summary}\\
Multidisciplinary software engineer and product leader with 10+ years of experience delivering robust web apps, automation tools, and cloud infrastructure. Blends technical depth with human-centered design. Specializes in backend Python development, DevOps pipelines, and cross-functional collaboration.

% -------------------- TECHNICAL SKILLS --------------------
\noindent
\textbf{\large Technical Skills}\\
\textbf{Languages:} Python, JS, Bash, C\#, SQL, R \\
\textbf{Frameworks:} Django, Flask, Node.js, React, ASP.NET \\
\textbf{Cloud/DevOps:} AWS (Lambda, EC2, S3, IAM, RDS), Serverless, GitHub Actions, Bitbucket Pipelines, Docker \\
\textbf{Monitoring/APM:} DataDog, Honeycomb, Stackdriver, CloudWatch, Sentry \\
\textbf{Tools:} Jira, Confluence, Postman, Slack, ArcGIS, PostgreSQL, Redis

% -------------------- EXPERIENCE --------------------
\noindent
\textbf{\large Experience}
\begin{itemize}[leftmargin=*]

\item \textit{Freelance Software Engineer}, Missoula, MT (2009--Present)
\begin{itemize}[leftmargin=1em]
  \item Developed Django/React web apps and custom Slack/Discord bots.
  \item Provided product strategy, MVP design, and full-stack engineering.
  \item Automated CI/CD workflows using GitHub Actions and Serverless.
  \item Contributed to open-source projects and mentored early-stage teams.
  \item \textit{Impact: Helped founders launch products and streamline operations.}
\end{itemize}

\item \textit{Software Engineer}, VYNYL (2021--2024)
\begin{itemize}[leftmargin=1em]
  \item Built AWS Lambda and Step Function pipelines for healthcare apps.
  \item Created mobile-responsive portals for Athena scheduling and Zoom visits.
  \item Implemented GitHub Actions CI/CD pipelines and unittest coverage.
  \item Developed Playwright-based tests and Python data validation scripts.
  \item \textit{Impact: Boosted reliability, testing, and developer velocity.}
\end{itemize}

\item \textit{Software Engineer}, Submittable (2019--2021)
\begin{itemize}[leftmargin=1em]
  \item Managed deployments via AWS CodePipeline and Serverless Framework.
  \item Built deploy automations with EventBridge and Lambda.
  \item Monitored production systems using CloudWatch and Slack integration.
  \item Maintained IAM roles, Route 53 DNS, and on-call troubleshooting.
  \item \textit{Impact: Improved uptime and release cadence by 30\%.}
\end{itemize}

\item \textit{CTO}, TOMIS (2016--2019)
\begin{itemize}[leftmargin=1em]
  \item Led product and engineering for a Python/Django and React SaaS app.
  \item Managed Jira workflows, QA, roadmap planning, and release pipelines.
  \item Integrated 3rd-party APIs and marketing automation tools.
  \item Oversaw monitoring (DataDog, Stackdriver), QA, and incident response.
  \item \textit{Impact: Built a modern platform that scaled to 100+ clients.}
\end{itemize}

\item \textit{Co-Founder/CTO}, dotmos (2015--2017)
\begin{itemize}[leftmargin=1em]
  \item Designed a media/search aggregator with Django, React, and Node.
  \item Created interactive dashboards and a scalable search UI.
  \item Managed deployments, documentation, and customer feedback loops.
  \item \textit{Impact: Unified social and search content into a single UX.}
\end{itemize}

\item \textit{Software Engineer}, Upstream Research (2015--2016)
\begin{itemize}[leftmargin=1em]
  \item Processed GIS datasets using ArcPy, Python, and Azure services.
  \item Built ASP.NET tools and PostgreSQL data pipelines.
  \item QA’d REST APIs with custom Python testing scripts.
  \item \textit{Impact: Enabled health/environmental analysis using geodata.}
\end{itemize}

\end{itemize}

% -------------------- EDUCATION --------------------
\noindent
\textbf{\large Education}\\
\textbf{University of Montana – Missoula, MT} \\
M.S. in Computer Science, 2014 — Focus: Machine Learning/AI \\
B.A. in Psychology, Minor in Math/Media Arts

\end{multicols}
\end{document}