% Me0wy Master Resume (AI + Data Infra + PM — Professional Focus)

\documentclass[10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[top=0.75in,bottom=0.75in,left=0.8in,right=0.8in]{geometry}
\usepackage{parskip}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}
\usepackage{fancyhdr} % <-- fancy header/footer
\setlist{nosep}
\pagenumbering{gobble}

% ----- Headings -----
\titleformat{\section}{\large\bfseries}{}{0pt}{}

% ----- Fancy header/footer -----
\pagestyle{fancy}
\fancyhf{} % clear defaults

% Header (Left): Name + compact contacts + © YEAR (Right)
\fancyhead[L]{\Huge Blair Gemmer \quad
  \small\{\href{https://blairgemmer.com}{blairgemmer.com} -
  \href{mailto:blair.gemmer@gmail.com}{blair.gemmer@gmail.com} -
  \href{tel:4062534962}{406.253.4962}\}}
\fancyhead[R]{\copyright\ \the\year}
\renewcommand{\headrulewidth}{1pt}

% Footer (Left): contacts + version
\renewcommand{\footrulewidth}{1pt}
\newcommand{\docversion}{v2025.10.14} % <-- update when you want
\fancyfoot[L]{\small\{\href{https://blairgemmer.com}{blairgemmer.com} -
  \href{mailto:blair.gemmer@gmail.com}{blair.gemmer@gmail.com} -
  \href{tel:4062534962}{406.253.4962}\}}
\fancyfoot[R]{\docversion}

\begin{document}

% ===== Header row removed (now handled by fancyhdr) =====

\section*{Summary}
Full-stack software engineer and technical product strategist specializing in automation, data infrastructure, and cloud-native backends. In the past five years: delivered healthcare and education platforms at scale, led DevOps for high-throughput releases, and built reliable integrations across AWS and modern Python stacks. I focus on systems that reduce toil, surface signal, and ship value quickly.

\section*{Core Skills}
\begin{itemize}[leftmargin=*]
  \item \textbf{Languages \& Frameworks:} Python, TypeScript/JavaScript, SQL, React, Next.js
  \item \textbf{Cloud \& Infrastructure:} AWS (Lambda, API Gateway, DynamoDB, RDS, EC2/ELB, Route~53, IAM/ACM, CloudWatch/X-Ray, EventBridge), CloudFormation, Serverless Framework, Docker, Kubernetes
  \item \textbf{Data \& Pipelines:} PostgreSQL, Redis, Snowflake, ETL/ingestion, PynamoDB
  \item \textbf{CI/CD \& Quality:} GitHub Actions, AWS CodePipeline, Bitbucket Pipelines, Tox, Poetry, Pytest, Playwright (E2E), integration/load tests in CI
  \item \textbf{Product \& Collaboration:} Jira, Linear, Confluence, Slack (bots/integrations)
  \item \textbf{AI \& Automation:} OpenAI/ChatGPT API, n8n, MCP, v0
\end{itemize}

\section*{Professional Experience}

\noindent\textbf{Freelance Software Engineer / Consultant} — Various Clients (Missoula, MT) \hfill 2009--Present\par
\emph{Data infrastructure, AI/automation integrations, and product delivery}\par
\begin{itemize}
  \item \textbf{Intrust Funding / Heaton Dainard (2024--2025):} Designed real-estate data ingestion and analytics pipelines integrating Snowflake with ATTOM and Salesforce; built Python ETL jobs, automated reporting, and implemented cost controls.
  \item \textbf{AI/Automation Integrations (2022--2025):} Built internal tools/bots using OpenAI API and n8n with Slack integrations to automate reporting, summarization, approvals, and human-in-the-loop workflows.
  \item \textbf{Product \& Delivery:} Built and launched cloud-native products and web apps for startups and personal ventures using AWS, React/Next.js, and Django/Flask. Drove end-to-end execution, from architecture and CI/CD automation to team building, project management, and technical operations.
  \item \textbf{Tool \textrightarrow{} outcome:} Snowflake + Python ETL \textrightarrow{} partitioned loads and scheduled tasks for leaner storage/compute; n8n + Slack \textrightarrow{} faster approvals and fewer manual steps.
  \item \textbf{Stack:} Python, React, Next.js, Django/Flask, PostgreSQL, Redis, Snowflake, REST APIs, GitHub Actions, Serverless approaches, OpenAI API, n8n.
\end{itemize}

\noindent\textbf{Software Engineer} — VYNYL, LLC (Remote) \hfill Mar~2021--Apr~2024\par
\emph{Healthcare (Happier Living) • Early Childhood Education (UCSF Multitudes)}\par
\begin{itemize}
  \item \textbf{Product \& Backend:} Built a mobile-responsive healthcare portal integrating Zoom consultations and Athena scheduling using Python on AWS (Lambda, API Gateway) with a modern web front end.
  \item \textbf{Data \& Validation (UCSF Multitudes):} Implemented Playwright E2E for critical flows; automated CSV\textrightarrow{}database validation in Python; added CI gates to block ingestion/UI regressions.
  \item \textbf{Observability \& Delivery:} Modeled operational data in DynamoDB via PynamoDB; AWS X-Ray + CloudWatch for tracing/metrics; Serverless Framework + GitHub Actions for reproducible envs and low-downtime deploys.
  \item \textit{Impact:} Delivered compliant, reliable clinician workflows and robust data validation across ingestion and UI.
  \item \textbf{Stack:} Python, React, AWS (Lambda, API Gateway, DynamoDB, CloudWatch, X-Ray), Serverless Framework, GitHub Actions, Playwright, Pandas, PynamoDB.
\end{itemize}

\newpage

\noindent\textbf{Software Engineer, DevOps} — Submittable, Inc. (Missoula, MT) \hfill Sep~2019--Mar~2021\par
\emph{DevOps • Release Engineering • Production Operations}\par
\begin{itemize}
  \item \textbf{Release Engineering:} Orchestrated SDLC and production releases using AWS CodePipeline; automated comms via GitHub releases and Slack; enforced branch hygiene and quality bars (Pytest/Tox) to stabilize daily deploy cadence.
  \item \textbf{IaC \& Environments:} Built and maintained test/prod with CloudFormation, Serverless Framework, EventBridge, and Lambda; managed IAM/ACM and Route~53; owned cert rotation and release gating.
  \item \textbf{Observability \& Ops:} CloudWatch dashboards/alerts; on-call with fast rollback/runbooks; Dependabot for dependency hygiene across repos.
  \item \textit{Impact:} Reduced deployment overhead ~30\% and moved from weekly to daily reliability-focused releases.
  \item \textbf{Stack:} AWS (CodePipeline, CloudFormation, Lambda, EventBridge, IAM, ACM, EC2, ELB, RDS, Route~53, CloudWatch), Serverless Framework, GitHub, Pytest, Tox.
\end{itemize}

\noindent\textbf{CTO} — TOMIS, Inc. \hfill Sep~2016--Jul~2019\par
\emph{Digital marketing and analytics platform}\par
\begin{itemize}
  \item \textbf{Technical Leadership:}
    \begin{itemize}[leftmargin=*,label=--]
      \item Owned product design from executive vision through technical implementation; authored detailed technical specifications and delivery plans.
      \item Led backend engineering for REST APIs (Python/Django); partnered with React teams on QA and key design decisions.
      \item Researched emerging tech; built prototypes and proofs-of-concept to de-risk roadmap bets.
    \end{itemize}
  \item \textbf{Project Management:}
    \begin{itemize}[leftmargin=*,label=--]
      \item Scrum Master: sprint planning, daily standups, retros; administered Jira (boards, workflows, triage) and Confluence docs.
      \item Managed Bitbucket repos and branching strategy; integrated Slack for release comms and team coordination.
      \item Authored release notes from Jira releases using Confluence templates; prioritized epics using Jira Next-Gen Kanban.
    \end{itemize}
  \item \textbf{DevOps:}
    \begin{itemize}[leftmargin=*,label=--]
      \item Enforced commit quality and code review processes; maintained feature/release/hotfix branching hygiene.
      \item Implemented Bitbucket Pipelines for automated testing on feature branches; tracked bugs/feedback with Usersnap.
    \end{itemize}
  \item \textbf{Site Reliability \& Observability:}
    \begin{itemize}[leftmargin=*,label=--]
      \item Production monitoring and tracing with Datadog \& Honeycomb; centralized logging and infra monitoring with Stackdriver/Datadog.
      \item Exception reporting via Sentry (with Jira integration); uptime and incident comms via UptimeRobot and Statuspage.io.
    \end{itemize}
  \item \textit{Impact:} Spearheaded a SaaS platform for tour operators that automated workflows and delivered actionable analytics.
  \item \textbf{Stack:} Python, Django, PostgreSQL; Bitbucket Pipelines; Jira, Confluence, Slack; Datadog, Honeycomb, Stackdriver, Sentry; Usersnap; UptimeRobot, Statuspage.io.
\end{itemize}

\noindent\textbf{Co-Founder / CTO} — dotmos, LLC \hfill Jul~2015--Jan~2017\par
\emph{Social/search aggregation product \& consulting}\par
\begin{itemize}
  \item Product/architecture for Django/Node/React stack; delivered core features and integrations; supported CI/CD and monitoring.
  \item \textbf{Stack:} Python/JavaScript, Django/Node/React, SQL; AWS/GCP (as applicable); CI/CD.
\end{itemize}

\noindent\textbf{Data Scientist / Software Engineer} — Upstream Research, Inc. \hfill Nov~2015--Sep~2016\par
\emph{Data and research workflows}\par
\begin{itemize}
  \item Implemented data processing automation and reporting pipelines; built internal dashboards/APIs.
  \item Built an ETL pipeline to generate ArcGIS layers from source datasets for geospatial visualization and analysis.
  \item \textbf{Stack:} Python, PostgreSQL, ETL tooling, Azure (admin), REST APIs; ArcGIS/ArcPy; ASP.NET MVC (C\#).
\end{itemize}

\section*{Additional Experience}
\noindent\textbf{Security Consultant} — LMG Security\par
\noindent\textbf{Senior Software Developer} — Hanna-James Enterprises

\section*{Education}
\textbf{M.S., Computer Science (AI/ML emphasis)} — University of Montana\par
\textbf{B.A., Psychology} — University of Montana \quad \emph{Minors: Mathematics, Media Arts}

% Optional creative one-liner (commented for professional focus)
% Performed extensively as a live streamer (Twitch) — bringing user empathy, systems discipline under pressure, and audience-driven iteration.

\end{document}
