% Resume.tex – One-page résumé (fits)
\documentclass[10pt]{article}

% --------------- Packages & Layout ---------------
\usepackage[top=1in,bottom=0.9in,left=1in,right=1in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{parskip}
\usepackage[hidelinks]{hyperref}
\usepackage{ragged2e}
\usepackage[none]{hyphenat}
\usepackage{fancyhdr}

% --------------- Global Tweaks ---------------
\hyphenpenalty=10000 \exhyphenpenalty=10000
\raggedbottom
\pagenumbering{gobble}

% Section spacing
\titlespacing*{\section}{0pt}{4pt}{2pt}

% Bulletless, *tighter* lists
\setlist[itemize]{label={},leftmargin=*,itemsep=1.5pt,topsep=1.5pt,parsep=0pt,partopsep=0pt}

% Heading styles
\titleformat{\section}{\Large\bfseries}{}{0em}{}
\titleformat{\subsection}{\normalsize\bfseries}{}{0em}{}

% --------------- Header & Footer ---------------
\pagestyle{fancy}
\renewcommand{\headrulewidth}{1pt}
\renewcommand{\footrulewidth}{1pt}

\fancyhead{}\fancyfoot{}
\fancyhead[L]{%
  \huge Blair Gemmer\quad
  \small\{\href{https://blairgemmer.com}{blairgemmer.com} -- %
  \href{mailto:blair.gemmer@gmail.com}{blair.gemmer@gmail.com} -- %
  406.253.4962\}\hfill ©~\the\year}
\fancyfoot[L]{%
  \small\{\href{https://blairgemmer.com}{blairgemmer.com} -- %
  \href{mailto:blair.gemmer@gmail.com}{blair.gemmer@gmail.com} -- %
  406.253.4962\}\hfill v2025.06.30}

% =================================================
\begin{document}
\RaggedRight

%%%%%%%%%%%%%%%%%%%% SUMMARY %%%%%%%%%%%%%%%%%%%%%%
\noindent\textbf{\large Summary}\\
Multidisciplinary software engineer \& product leader with 10\,+ years shipping production-grade web apps, automation pipelines, and cloud infrastructure. Expert in Python, Django/Flask, React, and AWS serverless; skilled at turning business goals into scalable, observable systems while mentoring cross-functional teams.

%%%%%%%%%%%%%%%% TECHNICAL SKILLS %%%%%%%%%%%%%%%%
{\small
\noindent\textbf{\large Technical Skills}\\
\textbf{Languages:} Python, JavaScript, Bash, C\#, SQL, R\\
\textbf{Frameworks:} Django, Flask, React, Node.js, ASP.NET\\
\textbf{Cloud/DevOps:} AWS (Lambda, Step Functions, S3, RDS, CloudFormation), GitHub Actions, Docker, Kubernetes, Serverless\\
\textbf{Monitoring/APM:} Datadog, Sentry, CloudWatch, X-Ray\\
\textbf{Databases/Cache:} PostgreSQL, RDS, S3, Redis, DynamoDB\\
\textbf{Collaboration:} Jira, Confluence, Slack, Git (GitHub/Bitbucket)
\normalsize}

%%%%%%%%%%%%%%%%% EXPERIENCE (10 yrs) %%%%%%%%%%%%
\noindent\textbf{\large Professional Experience}

\begin{itemize}
\item \textit{Freelance Software Engineer} \hfill Jan 2009–Present
  \begin{itemize}[leftmargin=1em]
    \item Built 20+ Django/React apps \& Slack/Discord bots; automated CI/CD with GitHub Actions (–60 \% deploy time).
    \item Guided founders on MVP scope, analytics, and product-market fit.
  \end{itemize}

\item \textit{Software Engineer} \textbf{\href{https://vynyl.com}{VYNYL, LLC}} \hfill Mar 2021–Apr 2024
  \begin{itemize}[leftmargin=1em]
    \item Built a HIPAA-compliant virtual-care portal (Lambda, SQS/SNS, Step Functions, S3, DynamoDB); deployed via Serverless Framework \& GitHub Actions.
    \item Added Playwright tests \& Python data-validation scripts for UCSF Multitudes, boosting data integrity.
    \item Instrumented X-Ray/CloudWatch dashboards; wrote runbooks; partnered with FE, QA, product to hit deadlines.
  \end{itemize}

\item \textit{Software Engineer} \textbf{\href{https://submittable.com}{Submittable, Inc.}} \hfill Sep 2019–Mar 2021
  \begin{itemize}[leftmargin=1em]
    \item Ran CI/CD with CodePipeline, CloudFormation, Serverless; automated Slack release notes \& Dependabot security fixes.
    \item Built EventBridge/Lambda automations, tuned IAM, managed SecOps on EC2/ELB/RDS; on-call responder for prod issues.
    \item Cut deploy overhead 30\% and shifted releases from weekly to daily, keeping near-24/7 uptime.
  \end{itemize}

\item \textit{CTO} \textbf{\href{https://tomis.tech}{TOMIS, Inc.}} \hfill Sep 2016–Jul 2019
  \begin{itemize}[leftmargin=1em]
    \item Launched a Django + React SaaS for tour-operator analytics; scaled to 100+ clients.
    \item Scrum Master—ran Jira, Confluence, Bitbucket; instituted Bitbucket Pipelines CI; wrote release notes.
    \item Led DevOps/SRE: Datadog, Honeycomb, Stackdriver, Sentry, UptimeRobot, Statuspage (99.99\% uptime).
  \end{itemize}

\item \textit{Co-Founder / CTO} \textbf{\href{https://dotmos.com}{dotmos, LLC}} \hfill Jul 2015–Jan 2017
  \begin{itemize}[leftmargin=1em]
    \item Architected a social-media/search-aggregation platform (Django, Node.js, React) integrating 10+ external APIs.
    \item Led a 5-person team; enforced code reviews, CI with DeployBot, Agile backlog in Asana.
    \item Used analytics + feedback for rapid feature iterations, boosting engagement for creators and users.
  \end{itemize}

\item \textit{Data Scientist \& Software Engineer} \textbf{\href{https://upstreamresearch.com}{Upstream Research, Inc.}} \hfill Nov 2015–Sep 2016
  \begin{itemize}[leftmargin=1em]
    \item Processed multi-GB geospatial data with Python/ArcPy; published ArcGIS services for state health dashboards.
    \item Built an ASP.NET MVC app + PostgreSQL functions; automated ETL \& REST endpoints, shrinking refreshes from days to hours.
    \item Deployed to Azure, load-tested APIs, and held 99.99\% uptime while handling support tickets and SLA compliance.
  \end{itemize}
\end{itemize}

%%%%%%%%%%%%%%%%%%%% EDUCATION %%%%%%%%%%%%%%%%%%%%
{\small
\noindent\textbf{\large Education}\\
\textbf{University of Montana - Missoula}: \\ \{2014\} M.S.\ Computer Science (ML/AI) \\ \{2010\} B.A.\ Psychology, Minor Mathematics \& Media Arts
\normalsize}

\end{document}
