\documentclass[10pt]{article}
\usepackage[margin=0.7in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}
\rfoot{\thepage}

\setlist[itemize]{noitemsep, topsep=0pt, label=--, leftmargin=1.5em}

\titleformat{\section}{\bfseries\Large}{}{0em}{}
\titleformat{\subsection}{\bfseries\normalsize}{}{0em}{}

\begin{document}

\begin{center}
    \textbf{Blair G.} \\
    your.email@example.com | (555) 555-5555 | Missoula, MT \\
    \href{https://yourportfolio.com}{yourportfolio.com} | \href{https://linkedin.com/in/yourlinkedin}{linkedin.com/in/yourlinkedin} | \href{https://github.com/yourgithub}{github.com/yourgithub}
\end{center}

\section*{Summary}
Multidisciplinary software engineer and product leader with over a decade of experience across startups, SaaS platforms, and freelance consulting. Passionate about Python, automation, and data-driven development. Strong foundation in product strategy, DevOps, and backend engineering.

\section*{Technical Skills}
\textbf{Languages:} Python, JavaScript, Bash, C\#, SQL, R \\
\textbf{Frameworks:} Django, Flask, React, Node.js, ASP.NET \\
\textbf{Cloud/DevOps:} AWS (Lambda, S3, EC2, IAM, Step Functions), GitHub Actions, Serverless, Docker, Bitbucket Pipelines \\
\textbf{Monitoring/APM:} DataDog, Honeycomb, Stackdriver, Sentry, CloudWatch \\
\textbf{Tools:} Jira, Confluence, ArcGIS, Redis, PostgreSQL, Slack

\section*{Experience}

\textit{Consultant, Software Engineer} \textbf{Independent Consulting \{Missoula, MT\}} \hfill May 2009 -- Present
\begin{itemize}
  \item Built and maintained full-stack web apps for local and global clients using Django/React.
  \item Delivered automation solutions, custom API integrations, and Discord/Slack bots.
  \item Advised founders on product roadmaps, MVPs, and technical strategy.
  \item \textit{\textbf{Impact:} Helped founders launch products and scale from zero to production.}
\end{itemize}

\textit{Software Engineer} \textbf{VYNYL \{Remote\}} \hfill March 2021 -- April 2024
\begin{itemize}
  \item Developed AWS Lambda-based infrastructure and Step Functions for a healthcare portal.
  \item Created CI/CD pipelines in GitHub Actions with unit/integration test coverage.
  \item Built Playwright integration tests for early learning tablet apps.
  \item \textit{\textbf{Impact:} Enhanced reliability and testing of critical healthcare/education apps.}
\end{itemize}

\textit{Software Engineer} \textbf{Submittable \{Missoula, MT\}} \hfill September 2019 -- March 2021
\begin{itemize}
  \item Deployed production systems using AWS CodePipeline, EventBridge, and Lambda.
  \item Maintained IAM policies, Route 53, RDS, and EC2 resources.
  \item Implemented monitoring/alerting with CloudWatch and on-call incident response.
  \item \textit{\textbf{Impact:} Improved release cadence and reduced downtime.}
\end{itemize}

\textit{CTO} \textbf{TOMIS \{Missoula, MT\}} \hfill September 2016 -- July 2019
\begin{itemize}
  \item Led product strategy and full-stack development for SaaS serving tour operators.
  \item Built Django/React platform with 3rd-party API integrations (analytics, bookings).
  \item Owned infrastructure, QA, documentation, and agile project management.
  \item \textit{\textbf{Impact:} Scaled platform to 100+ clients with automated marketing tools.}
\end{itemize}

\textit{Co-Founder \& CTO} \textbf{dotmos \{Missoula, MT\}} \hfill July 2015 -- January 2017
\begin{itemize}
  \item Architected media discovery platform with Django, Node.js, and React.
  \item Built content aggregation pipelines, search features, and dashboards.
  \item Managed DevOps, product decisions, and documentation.
\end{itemize}

\textit{Software Engineer} \textbf{Upstream Research \{Missoula, MT\}} \hfill November 2015 -- September 2016
\begin{itemize}
  \item Created ArcGIS data layers from diverse federal/state datasets.
  \item Wrote Python/ArcPy scripts and developed ASP.NET tools.
  \item Handled QA, server administration, and customer issue debugging.
  \item \textit{\textbf{Impact:} Unified diverse datasets into actionable insights to streamline planning and improve services.}
\end{itemize}

\section*{Education}
\textbf{University of Montana \{Missoula, MT\}} \\
M.S. in Computer Science (Machine Learning \& AI focus), 2014 \\
B.A. in Psychology, Minor in Mathematics \& Media Arts

\end{document}
