\documentclass[10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[top=0.75in,bottom=0.75in,left=0.8in,right=0.8in]{geometry}
\usepackage{parskip}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}
\usepackage{fancyhdr}
\setlist{nosep}
\pagenumbering{gobble}
\titleformat{\section}{\large\bfseries}{}{0pt}{}

% ----- Fancy header/footer -----
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\Huge Blair Gemmer \quad
  \small\{\href{https://blairgemmer.com}{blairgemmer.com} -
  \href{mailto:blair.gemmer@gmail.com}{blair.gemmer@gmail.com} -
  \href{tel:4062534962}{406.253.4962}\}}
\fancyhead[R]{\copyright\ \the\year}
\renewcommand{\headrulewidth}{1pt}
\renewcommand{\footrulewidth}{1pt}
\newcommand{\docversion}{v2025.10.15}
\fancyfoot[L]{\small\{\href{https://blairgemmer.com}{blairgemmer.com} -
  \href{mailto:blair.gemmer@gmail.com}{blair.gemmer@gmail.com} -
  \href{tel:4062534962}{406.253.4962}\}}
\fancyfoot[R]{\docversion}

\begin{document}

\section*{Summary}
Full-stack software engineer and technical product strategist specializing in automation, delivery systems, and cloud infrastructure on AWS. In the past five years: raised deploy cadence, standardized CI/CD and IaC, and improved reliability with clear observability. I focus on systems that reduce toil, surface signal, and ship value quickly. Recently, I have been leveraging AI resources and tools such as ChatGPT, n8n, MCP, and Linear to maintain quality while reducing research and development costs.

\section*{Core Skills}
\begin{itemize}[leftmargin=*]
  \item \textbf{CI/CD and Quality:} AWS CodePipeline, GitHub Actions, Bitbucket Pipelines, Tox, Poetry, Pytest, Playwright
  \item \textbf{IaC and Environments:} CloudFormation, Serverless Framework; IAM/ACM, Route 53
  \item \textbf{Observability and SRE:} CloudWatch, X-Ray, Datadog, Honeycomb, Sentry; runbooks and rollback paths
  \item \textbf{Cloud and Infrastructure:} Lambda, EventBridge, EC2/ELB, RDS, DynamoDB
  \item \textbf{Languages and Frameworks:} Python, TypeScript/JavaScript, SQL; React, Next.js
\end{itemize}

\section*{Selected Experience}
\noindent\textbf{Freelance} \textit{Software Engineer and Consultant} \hfill May 2009 - Present\par
\begin{itemize}
  \item Automated delivery and ops for small teams; GitHub Actions pipelines and serverless deployments on AWS.
  \item AI and automation integrations: OpenAI API and n8n with Slack bots for approvals, summaries, and internal tools.
\end{itemize}

\noindent\textbf{VYNYL} \textit{Software Engineer} \hfill Mar 2021 - Apr 2024\par
\begin{itemize}
  \item Reproducible environments with Serverless Framework; GitHub Actions pipelines; CloudWatch and X-Ray across Lambda services.
\end{itemize}

\noindent\textbf{Submittable} \textit{Software Engineer in DevOps} \hfill Sep 2019 - Mar 2021\par
\begin{itemize}
  \item CI/CD with CodePipeline and CloudFormation; EventBridge workflows; quality bars with Pytest and Tox; certs and networking with ACM and Route 53.
  \item On-call with fast rollback; moved cadence from weekly to daily and reduced release overhead about 30 percent.
\end{itemize}

\noindent\textbf{TOMIS} \textit{CTO} \hfill Sep 2016 - Jul 2019\par
\begin{itemize}
  \item Delivery and reliability practices: Bitbucket Pipelines, Jira, Confluence, Usersnap, Sentry; monitoring with Datadog and Honeycomb; incident comms via Statuspage and UptimeRobot.
\end{itemize}

\section*{Education}
M.S., Computer Science (AI/ML emphasis) — University of Montana \\
B.A., Psychology — University of Montana \quad \emph{Minors: Mathematics, Media Arts}

\end{document}
