\documentclass[10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[top=0.75in,bottom=0.75in,left=0.8in,right=0.8in]{geometry}
\usepackage{parskip}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}
\usepackage{fancyhdr}
\setlist{nosep}
\pagenumbering{gobble}
\titleformat{\section}{\large\bfseries}{}{0pt}{}

% ----- Fancy header/footer -----
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\Huge Blair Gemmer \quad
  \small\{\href{https://blairgemmer.com}{blairgemmer.com} -
  \href{mailto:blair.gemmer@gmail.com}{blair.gemmer@gmail.com} -
  \href{tel:4062534962}{406.253.4962}\}}
\fancyhead[R]{\copyright\ \the\year}
\renewcommand{\headrulewidth}{1pt}
\renewcommand{\footrulewidth}{1pt}
\newcommand{\docversion}{v2025.10.15}
\fancyfoot[L]{\small\{\href{https://blairgemmer.com}{blairgemmer.com} -
  \href{mailto:blair.gemmer@gmail.com}{blair.gemmer@gmail.com} -
  \href{tel:4062534962}{406.253.4962}\}}
\fancyfoot[R]{\docversion}

\begin{document}

\section*{Summary}
Full-stack software engineer and technical product strategist specializing in automation, data infrastructure, and cloud-native backends. In the past five years: delivered healthcare and education platforms at scale, led DevOps for high-throughput releases, and built reliable integrations across AWS and modern Python stacks. I focus on systems that reduce toil, surface signal, and ship value quickly. Recently, I have been leveraging AI resources and tools such as ChatGPT, n8n, MCP, and Linear to maintain quality while reducing research and development costs.

\section*{Core Skills}
\begin{itemize}[leftmargin=*]
  \item \textbf{Languages and Frameworks:} Python, TypeScript/JavaScript, SQL, React, Next.js
  \item \textbf{Cloud and Infrastructure:} AWS (Lambda, API Gateway, DynamoDB, RDS, EC2/ELB, Route 53, IAM/ACM, CloudWatch/X-Ray, EventBridge), CloudFormation, Serverless Framework, Docker, Kubernetes
  \item \textbf{Data and Pipelines:} PostgreSQL, Redis, Snowflake, ETL and ingestion, PynamoDB
  \item \textbf{CI/CD and Quality:} GitHub Actions, AWS CodePipeline, Tox, Poetry, Pytest, Playwright
\end{itemize}

\section*{Selected Experience}
\noindent\textbf{Freelance} \textit{Software Engineer and Consultant} \hfill May 2009 - Present\par
\begin{itemize}
  \item Cloud-native products and APIs on AWS with Python and React/Next.js; owned architecture, CI/CD, and technical operations end to end.
  \item Intrust Funding / Heaton Dainard (2024 - 2025): Snowflake and Python ETL from ATTOM and Salesforce; scheduled loads, automated reporting, cost controls.
  \item AI and automation integrations (2022 - 2025): OpenAI API and n8n with Slack bots for approvals and summaries with people in the loop when needed.
\end{itemize}

\noindent\textbf{VYNYL} \textit{Software Engineer} \hfill Mar 2021 - Apr 2024\par
\begin{itemize}
  \item Built AWS services for a healthcare portal integrating Zoom and Athena on Lambda and API Gateway; modeled data in DynamoDB via PynamoDB; observability with X-Ray and CloudWatch; CI with Serverless Framework and GitHub Actions.
  \item UCSF Multitudes: Playwright E2E tests and Python automation to validate CSV to database ingest with CI gates.
\end{itemize}

\noindent\textbf{Submittable} \textit{Software Engineer in DevOps} \hfill Sep 2019 - Mar 2021\par
\begin{itemize}
  \item Standardized CodePipeline and CloudFormation; EventBridge workflows; Pytest and Tox quality gates; GitHub and Slack release comms.
  \item Result: weekly to daily deploys and about 30 percent less release overhead.
\end{itemize}

\noindent\textbf{TOMIS} \textit{CTO} \hfill Sep 2016 - Jul 2019\par
\begin{itemize}
  \item Took founder ideation to marketable product: led specs, architecture, and delivery for a SaaS platform for tour operators (Python/Django, React).
  \item SDLC and reliability: Bitbucket Pipelines, Jira, Confluence, Usersnap, Sentry; monitoring with Datadog and Honeycomb; incident comms via Statuspage and UptimeRobot.
\end{itemize}

\section*{Education}
M.S., Computer Science (AI/ML emphasis) — University of Montana \\
B.A., Psychology — University of Montana \quad \emph{Minors: Mathematics, Media Arts}

\end{document}
