\documentclass[a4paper,10.5pt]{article}
\usepackage[left=1in, right=1in, top=1in, bottom=1in]{geometry}
\usepackage{setspace}

% Define Variables for Easy Customization
\newcommand{\applicantName}{Blair Gemmer}
\newcommand{\applicantEmail}{blair.gemmer@gmail.com }
\newcommand{\applicantPhone}{406.253.4962 }
\newcommand{\linkedinURL}{\texttt{linkedin.com/in/blairgemmer}}
\newcommand{\applicationDate}{February 3, 2025}
\newcommand{\companyName}{Company Name}
\newcommand{\hiringManager}{Hiring Manager}
\newcommand{\companyAddress}{Company Address}
\newcommand{\jobTitle}{Job Title}
\newcommand{\productName}{product name}

\begin{document}

\begin{flushleft}
\textbf{\large \applicantName} \\
\applicantEmail \textbar\ \applicantPhone \textbar\ \linkedinURL \\
\textbf{\applicationDate}  
\end{flushleft}

\begin{flushleft}
\textbf{\hiringManager} \\
\companyName \\  
\companyAddress  
\end{flushleft}

\vspace{0.5cm}

\noindent
\textbf{Re: \jobTitle{} -- \companyName{}}

\vspace{0.5cm}

\noindent
Dear \hiringManager,

\vspace{0.5cm}

I’m excited to apply for the \textbf{\jobTitle} position at \textbf{\companyName}. As a seasoned engineer with a passion for building scalable, high-performance systems, I am eager to contribute my expertise to a company that values innovation, reliability, and efficiency. 

With a background in software architecture, cloud infrastructure, and distributed systems, I thrive in designing solutions that enhance scalability, security, and maintainability. My experience leading engineering teams, defining technical strategy, and optimizing system performance aligns well with \companyName’s commitment to engineering excellence. I am excited about the opportunity to bring my skills to a dynamic and forward-thinking team.


\vspace{0.5cm}

\noindent
\textbf{Why I’m a Strong Fit for \companyName}

Over the past \textbf{10+ years}, I’ve worked with \textbf{multiple startups and tech-driven companies}, bridging the gap between technical execution and scalable architecture. My experience spans \textbf{software development, DevOps, distributed systems, and cloud infrastructure}, giving me the ability to lead engineering teams while keeping reliability, performance, and business goals at the forefront. I specialize in \textbf{building and optimizing high-performance systems}, making me an ideal fit for a technical leadership role in a company like \companyName.

\begin{itemize}
    \item \textbf{Deep Technical Expertise}: My \textbf{MS in Computer Science with an emphasis on AI and machine learning} has given me a strong foundation in designing scalable architectures, optimizing performance, and implementing automation—key aspects of modern software engineering.
    \item \textbf{Scalability and Cloud Infrastructure}: I have extensive experience in \textbf{cloud platforms (AWS, GCP, Azure)}, microservices, and \textbf{orchestration tools} like Kubernetes and Docker, ensuring that systems remain robust and scalable.
    \item \textbf{Technical Leadership \& Strategy}: I have \textbf{led engineering teams, defined technical roadmaps, and driven large-scale projects} that required balancing innovation with real-world performance constraints.
    \item \textbf{Optimizing Performance and Reliability}: My expertise in \textbf{distributed systems, caching strategies, and database optimizations} has enabled me to build systems that scale efficiently while maintaining high availability.
\end{itemize}

\vspace{0.5cm}

\noindent
\textbf{Why \companyName?}

\companyName{} has long been at the forefront of \textbf{engineering excellence and scalable infrastructure}, and I’m excited about the opportunity to contribute to a team that values \textbf{innovation, performance, and reliability}. The chance to \textbf{lead architectural decisions, mentor engineers, and drive technical excellence} aligns perfectly with my experience and aspirations.


\vspace{0.5cm}

I’d love the opportunity to discuss how my experience and skills can help drive innovation and scale at \companyName{}. Thank you for your time, and I look forward to the possibility of contributing to \textbf{\companyName’s mission to build world-class engineering solutions}.



\vspace{0.5cm}

\noindent
\textbf{Best regards,} \\
\applicantName

\end{document}
